\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
Explain hoverables better

The polymorphic \texttt{a} type can serve as an identifier. The first
value supplies the default value of \texttt{events} (signals must always
be defined and so a default value is required). The returned record
includes the \texttt{events} signal and the \texttt{hoverable}
function, which in general may be applied multiple times so that
multiple elements report their hover information on \texttt{events}. The
\texttt{(Bool -> a)} is used to identify which element
experienced the event; a common use is \texttt{a = (Int, Bool)} where
the integer identifies the element and the boolean is the event.
Additionally, \texttt{hoverables} is used to implement
\texttt{hoverable}:

@@

It ignores the polymorphism (\texttt{a = Bool}) and instead create a
boolean signal that is originally false and use the identity function to
not alter the hoverable information. With a simple change, we can create
a function that acts on \texttt{Signal Element} instead of
\texttt{Element}:

>>>>

A typical use of \texttt{hoverables} is as follows. An initial
\texttt{a} is supplied that becomes the default value of
\texttt{events}. If \texttt{hoverable} is never applied, \texttt{events}
is constant. If it is, the \texttt{Element} argument of
\texttt{hoverable} in the record acts much like it does in
\texttt{hoverable} the top-level combinator: provides the static visual
appearance of the result \texttt{Element}, which also has hover
detection added. Hover events are boolean, so the function argument is
called on every such event to produce an \texttt{a} that becomes an
event on \texttt{events}.

What gives \texttt{hoverables} its plural name is that the record's
\texttt{hoverable} may be applied multiple times so that multiple
elements report their hover information on \texttt{events}. The
polymorphic \texttt{a} type exists to uniquely identify each element,
though it is also common for the \texttt{a} to also include the boolean
event. The simplest choice of \texttt{a} is simply \texttt{Bool}, and
this allows \texttt{hoverables} to implement \texttt{hoverable}:

@@

The \texttt{a -> Bool} function trivially becomes the identity. With a simple
change, we can create a function that acts on \texttt{Signal Element} instead of
\texttt{Element}:
